Variance in scarid grazing behavior across Caribbean reef sites

### 2019-04-19 r/Ch2 outline_V3.Rmd
4.18

fr_qup <- 
  ggplot(filter(sum_ssp, species_code == "qup" & phase == "i"), 
         aes(x=factor(site, levels = sum_site$site), y=fr_mean)) +
  geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
  geom_errorbar(aes(ymin=fr_mean-fr_se, ymax=fr_mean+fr_se), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_brewer(palette = "Blues") +
  #geom_abline(slope=0, intercept=ref_qup15,  col = "red",lty=2) +
  #geom_abline(slope=0, intercept=ref_qup25,  col = "red",lty=2) +
  #ylim(0, 50) +
  labs(y = "Feeding rate \n (bites/min)", 
       title = "S. vetula") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5, face = "italic"),
        plot.margin = margin(5, 0, 0, 5, unit = "pt"),
        strip.text = element_text(face = "italic"), 
        axis.text.x=element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=10),
        legend.position = "none")

@@

br_qup <- 
  ggplot(filter(sum_ssp, species_code == "qup" & phase == "i"), 
         aes(x=factor(site, levels = sum_site$site), y=br_mean)) +
  geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
  geom_errorbar(aes(ymin=br_mean-br_se, ymax=br_mean+br_se), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_brewer(palette = "Blues") +
  labs(y = "Bite rate \n(bites/sec)", 
       x = "", 
       title = "") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5),
        plot.margin = margin(0, 0, 0, 5, unit = "pt"),
        strip.text = element_text(face = "italic"), 
        axis.text.x=element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=10),
        legend.position = "none")

@@

gfrac_qup <- 
  ggplot(filter(sum_ssp, species_code == "qup" & phase == "i"), 
         aes(x=factor(site, levels = sum_site$site), y=g_frac_mean)) +
  geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
  geom_errorbar(aes(ymin=g_frac_mean-g_frac_se, ymax=g_frac_mean+g_frac_se), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_brewer(palette = "Blues") +
  labs(y = "Time grazing \n(fraction)", 
       x = "", 
       title = "") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5),
        plot.margin = margin(0, 0, 0, 5, unit = "pt"),
        strip.text = element_text(face = "italic"), 
        axis.text.x=element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=10),
        legend.position = "none")

@@

fi_qup <- 
  ggplot(filter(sum_ssp, species_code == "qup" & phase == "i"), 
         aes(x=factor(site, levels = sum_site$site), y=for_bites_mean)) +
  geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
  geom_errorbar(aes(ymin=for_bites_mean-for_bites_se, ymax=for_bites_mean+for_bites_se), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_brewer(palette = "Blues") +
  labs(y = "Grazing concentration\n(bites/foray)", 
       x = "", 
       title = "") +
  theme_bw() + 
  theme(plot.margin = margin(0, 0, 0, 5, unit = "pt"),
        axis.title.y = element_text(size=10),
        axis.text.x = element_text(angle = 45, hjust = 1, size=7),
        legend.position = "none")

@@

grid.arrange(
  arrangeGrob(fr_qup, fr_stop, gfrac_qup, gfrac_stop, fi_qup, fi_stop, ncol=2, heights = c(1,1,1.5)), 
              arrangeGrob(legend), 
              ncol=2, widths = c(5,1))

```

>>>>

fr_qup <- 
  ggplot(filter(sum_ssp, species_code == "qup" & phase == "i"), 
         aes(x=factor(site, levels = sum_site$site), y=fr_mean)) +
  geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
  geom_errorbar(aes(ymin=fr_mean-fr_se, ymax=fr_mean+fr_se), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_brewer(palette = "Blues") +
  #geom_abline(slope=0, intercept=ref_qup15,  col = "red",lty=2) +
  #geom_abline(slope=0, intercept=ref_qup25,  col = "red",lty=2) +
  #ylim(0, 50) +
  labs(y = "Feeding rate \n (bites/min)", 
       title = "S. vetula") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5, face = "italic"),
        plot.margin = margin(5, 0, 0, 5, unit = "pt"),
        strip.text = element_text(face = "italic"), 
        axis.text.x=element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=8),
        legend.position = "none")

@@

br_qup <- 
  ggplot(filter(sum_ssp, species_code == "qup" & phase == "i"), 
         aes(x=factor(site, levels = sum_site$site), y=br_mean)) +
  geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
  geom_errorbar(aes(ymin=br_mean-br_se, ymax=br_mean+br_se), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_brewer(palette = "Blues") +
  labs(y = "Bite rate \n(bites/sec)", 
       x = "", 
       title = "") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5),
        plot.margin = margin(0, 0, 0, 5, unit = "pt"),
        strip.text = element_text(face = "italic"), 
        axis.text.x=element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=8),
        legend.position = "none")

@@

gfrac_qup <- 
  ggplot(filter(sum_ssp, species_code == "qup" & phase == "i"), 
         aes(x=factor(site, levels = sum_site$site), y=g_frac_mean)) +
  geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
  geom_errorbar(aes(ymin=g_frac_mean-g_frac_se, ymax=g_frac_mean+g_frac_se), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_brewer(palette = "Blues") +
  labs(y = "Time grazing \n(fraction)", 
       x = "", 
       title = "") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5),
        plot.margin = margin(0, 0, 0, 5, unit = "pt"),
        strip.text = element_text(face = "italic"), 
        axis.text.x=element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=8),
        legend.position = "none")

@@

fi_qup <- 
  ggplot(filter(sum_ssp, species_code == "qup" & phase == "i"), 
         aes(x=factor(site, levels = sum_site$site), y=for_bites_mean)) +
  geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
  geom_errorbar(aes(ymin=for_bites_mean-for_bites_se, ymax=for_bites_mean+for_bites_se), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_brewer(palette = "Blues") +
  labs(y = "Foray length\n(bites/foray)", 
       x = "", 
       title = "") +
  theme_bw() + 
  theme(plot.margin = margin(0, 0, 0, 5, unit = "pt"),
        axis.title.y = element_text(size=8),
        axis.text.x = element_text(angle = 45, hjust = 1, size=7),
        legend.position = "none")

@@

grid.arrange(
  arrangeGrob(fr_qup, fr_stop, gfrac_qup, gfrac_stop, br_qup, br_stop, fi_qup, fi_stop, ncol=2, heights = c(1.5,1.5,1.5,3)), 
              arrangeGrob(legend), 
              ncol=2, widths = c(5,1))

g <- arrangeGrob(
  arrangeGrob(fr_qup, fr_stop, gfrac_qup, gfrac_stop, br_qup, br_stop, fi_qup, fi_stop, ncol=2, heights = c(1,1,1,1.5)), 
              arrangeGrob(legend), 
              ncol=2, widths = c(5,1))

ggsave(here("figs/behavior_panel.png"),g)
```
